Pillar 2 - Topic Modeling

### 2019-01-15 Pillar 2 - Topic Modeling.Rmd
include rm()

```{r compute_tf_idf}
compute_tf_idf <- function(data) data %>%
                                   count(Code, word) %>%
                                   bind_tf_idf(term = word, document = Code, n = n)

tf_idf_description <- compute_tf_idf(filter(d_description, `Calendar Year` == "2018-2019"))
tf_idf_overview <- compute_tf_idf(filter(d_overview, `Calendar Year` == "2018-2019"))
tf_idf_manual <- compute_tf_idf(d_manual)
```

@@

set.seed(123)
tf_idf_manual %>%
  prepare_tf_idf_course %>%
  plot_tf_idf(plot_id = "Course_manual")
```

## Cluster Level
```{r tf-idf per cluster}
prepare_tf_idf_cluster <- function(data) data %>%
                                           left_join(select(d_course, Code, Cluster), by = "Code") %>%
                                           filter(!is.na(Cluster)) %>%
                                           rename(facet = Cluster) %>%
                                           group_by(facet, word) %>%
                                             summarise(tf_idf = sum(tf_idf),
                                                       n = sum(n)) %>%
                                             filter(n >= 10) %>%
                                             top_n(10, tf_idf) %>%
                                           ungroup

@@

tf_idf_manual %>%
  prepare_tf_idf_cluster %>%
  plot_tf_idf(plot_id = "Cluster_manual")
```

## Concentration Level

# LDA
hist
## Fitting Model
```{r}
d_overview_cast <- d_overview %>%
  count(Code, word, sort = T) %>%
  cast_dtm(Code,word, n)
```

```{r}
LDA_10 <- LDA(d_overview, k = 10, control = list(seed = 123))
LDA_17 <- LDA(d_overview, k = 17, control = list(seed = 123))
LDA_25 <- LDA(d_overview, k = 25, control = list(seed = 123))
```

>>>>

```{r compute_tf_idf, cache = TRUE}
compute_tf_idf <- function(data) data %>%
                                   count(Code, word) %>%
                                   bind_tf_idf(term = word, document = Code, n = n)

tf_idf_description <- compute_tf_idf(filter(d_description, `Calendar Year` == "2018-2019"))
tf_idf_overview    <- compute_tf_idf(filter(d_overview, `Calendar Year` == "2018-2019"))
tf_idf_manual      <- compute_tf_idf(d_manual)

rm(compute_tf_idf())
```

@@

set.seed(123)
tf_idf_manual %>%
  prepare_tf_idf_course %>%
  plot_tf_idf(plot_id = "Course_manual")

rm(prepare_tf_idf_course)
```

## Cluster Level
```{r tf-idf per cluster, cache = TRUE}
prepare_tf_idf_cluster <- function(data) data %>%
                                           left_join(select(d_course, Code, Cluster), by = "Code") %>%
                                           filter(!is.na(Cluster)) %>%
                                           rename(facet = Cluster) %>%
                                           group_by(facet, word) %>%
                                             summarise(tf_idf = sum(tf_idf),
                                                       n = sum(n)) %>%
                                             filter(n >= 10) %>%
                                             top_n(10, tf_idf) %>%
                                           ungroup

@@

tf_idf_manual %>%
  prepare_tf_idf_cluster %>%
  plot_tf_idf(plot_id = "Cluster_manual")

rm(prepare_tf_idf_cluster)
```

## Concentration Level
```{r, cache = TRUE}
prepare_tf_idf_concentration <- function(data) data %>%
                                                 left_join(select(d_course, Code, Concentration, `Concentration (additional)`), by = "Code") %>%
                                                 filter(!is.na(Concentration)) %>%
                                                 gather(X, Concentration, Concentration, `Concentration (additional)`, na.rm = TRUE) %>%
                                                 rename(facet = Concentration) %>%
                                                 group_by(facet, word) %>%
                                                   summarise(tf_idf = sum(tf_idf),
                                                             n = sum(n)) %>%
                                                   filter(n >= 10) %>%
                                                   top_n(10, tf_idf) %>%
                                                 ungroup

tf_idf_description %>%
  prepare_tf_idf_concentration %>%
  plot_tf_idf(plot_id = "Concentration_description")

tf_idf_overview %>%
  prepare_tf_idf_concentration %>%
  plot_tf_idf(plot_id = "Concentration_overview")

tf_idf_manual %>%
  prepare_tf_idf_concentration %>%
  plot_tf_idf(plot_id = "Concentration_manual")

rm(prepare_tf_idf_concentration, plot_tf_idf,
   tf_idf_description, tf_idf_overview, tf_idf_manual)
```

# LDA
## Fitting Model
```{r, eval = FALSE}
d_overview_cast <- d_overview %>%
  count(Code, word, sort = T) %>%
  cast_dtm(Code,word, n)
```

```{r, eval = FALSE}
LDA_10 <- LDA(d_overview, k = 10, control = list(seed = 123))
LDA_17 <- LDA(d_overview, k = 17, control = list(seed = 123))
LDA_25 <- LDA(d_overview, k = 25, control = list(seed = 123))
```
